Article counts per year figure

### 2022-02-02 article-counts-per-year-figure.Rmd
rendered Rmd to get figs

```{r}
library(dplyr)
dat <- readxl::read_xlsx(path = "data/publication-counts.xlsx", sheet = "counts")
dat %>%
  ggplot2::ggplot(ggplot2::aes(x = year, y = mrcount)) + ggplot2::geom_bar(stat = "identity")
```

```{r}
dat %>%
  ggplot2::ggplot(ggplot2::aes(x = year, y = gwascount)) + ggplot2::geom_bar(stat = "identity")

@@

>>>>

```{r}
library(magrittr)
dat <- readxl::read_xlsx(path = "data/publication-counts.xlsx", sheet = "counts")
dat %>%
  ggplot2::ggplot(ggplot2::aes(x = year, y = mrcount)) + ggplot2::geom_bar(stat = "identity")
ggplot2::ggsave("figures/mr-counts.png")
```

```{r}
dat %>%
  ggplot2::ggplot(ggplot2::aes(x = year, y = gwascount)) + ggplot2::geom_bar(stat = "identity")
ggplot2::ggsave("figures/gwas-counts.png")

@@

```{r}
dat %>%
  tidyr::pivot_longer(!year) %>%
  ggplot2::ggplot(ggplot2::aes(x = year, y = value, colour = name)) + ggplot2::geom_point()
ggplot2::ggsave("figures/mr-gwas-counts-scatter.png")
```
